%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Arif Gencosmanoglu} \\
  \href{https://github.com/0014}{github.com/0014} & Email : \href{mailto:a.gencosmanoglu@gmail.com}{a.gencosmanoglu@gmail.com}\\
  \href{https://linkedin.com/in/arif-gencosmanoglu-bb1929a2/}{linkedin.com/in/arif-gencosmanoglu-bb1929a2} & Mobile : +1 (862) 324 - 3377 
\end{tabular*}

%-----------INTRODUCTION-----------------
\vspace{0.2in}
\section*{Summary}
Innovative and impact-driven software engineer with 10+ years of experience in full-cycle software development, cloud infrastructure, and modern architectures. Proven success in leading legacy migrations, deploying microservices on Kubernetes, and launching production-ready platforms. Skilled at translating complex technical concepts, mentoring teams, and optimizing delivery pipelines. Passionate about emerging technologies including AI, blockchain, and DevOps.


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {New Jersey Institute of Technology (NJIT)}{Newark, NJ}
      {Master of Science in Computer Science}{Sep. 2019}
    \resumeSubheading
      {Istanbul Technical University (ITU)}{Istanbul, Turkiye}
      {Bachelor of Engineering in Electrical and Electronics}{Aug. 2014}
      \resumeItemListStart
        \resumeItem{\href{https://web.itu.edu.tr/~orssi/thesis/2014/ArifGencosmanoglu_bit.pdf}{Thesis}}
          {Design and Implementation of a Crypto Processor in CISC Architecture}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Azenta Life Sciences}{South Plainfield, NJ}
      {Software Engineer}{Jun 2022 - Present}
      \resumeItemListStart
        \resumeItem{.NET Migration}
          {Led the company-wide migration from legacy .NET Framework (web, WPF, API) to .NET Core using YARP reverse proxy for seamless interoperability.}
        \resumeItem{Microservice Architecture}
          {Designed and drove adoption of microservice architecture deployed on Kubernetes; created the first production-ready microservice as a reusable template.}
          \resumeItem{Kubernetes Enablement}
          {Collaborated with DevOps to build scalable Kubernetes clusters using Rancher and trained 30+ developers on container orchestration and Rancher UI.}
          \resumeItem{CI/CD Automation}
          {Implemented CI/CD pipelines for legacy and modern apps, reducing manual deployment time by 2+ hours daily per developer.}
          \resumeItem{Workflow Standardization}
          {Standardized workflows via GitLab tagging and branch-based deployments.}
          \resumeItem{UI Testing}
          {Evaluated Selenium, Playwright, and Rapise for UI testing; led company-wide adoption of Rapise, now achieving 75\%+ test coverage.}
      \resumeItemListEnd

    \resumeSubheading
      {Legal Services of New Jersey}{Edison, NJ}
      {Senior Software Engineer}{Mar 2020 - Jun 2022}
      \resumeItemListStart
        \resumeItem{Intake System}
          {Rebuilt the statewide legal intake system used daily by 100+ professionals.}
        \resumeItem{Conference Platform}
          {Built a modular conference system using .NET Core and Angular, supporting event creation, scheduling, and management. Implemented authentication, role-based access, internal notifications and integrated a payment system using Stripe APIs.}
        \resumeItem{Tech Evaluation}
          {Conducted R\&D on Docassemble and Umbraco CMS, leading to successful adoptions.}
      \resumeItemListEnd

    \resumeSubheading
      {Astrodyne TDI}{Hackettstown, NJ}
      {Software Developer}{Jun 2017 - Mar 2020}
      \resumeItemListStart
        \resumeItem{App Development}
          {Built 20+ internal applications using .NET Core, Angular, and DevExpress; created a reusable API framework for internal use.}
        \resumeItem{Legacy Modernization}
          {Maintained legacy C++ and Delphi systems while modernizing UIs for better usability and consistency.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Startup Platform}
      {Co-founded \textit{Wherezitz}, a social discovery platform built with .NET Core and Angular. Managed a remote team of 4, set up CI/CD with GitHub Actions, and integrated AWS, Azure, and Firebase. Launched MVP and pitched to investors; live at \href{https://wherezitz.com/}{wherezitz.com} and \href{https://wherezitz.app/}{wherezitz.app}. }
    \resumeSubItem{Tutoring Platform}
      {Built a custom platform for \textit{Shooting for Stars Tutoring} serving 60+ tutors and generating \$800–\$1,000/month. Integrated OpenAI APIs and automation bots to streamline operations. Live at \href{https://shootingforstarstutoring.com/}{shootingforstarstutoring.com}.}
    \resumeSubItem{Client Websites}
      {Found and managed clients for custom web development projects. Represented overseas developers, collected requirements, and served as the primary point of contact between developers and business owners. Delivered responsive and SEO-friendly websites for small US businesses, including \href{https://redstonedeveloper.com/}{redstonedeveloper.com}, \href{https://ottofloors.com/}{ottofloors.com}, and \href{https://ottotile.com/}{ottotile.com}. }
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item
     \textbf{Languages}: {C\#, TypeScript, JavaScript, SQL, HTML, CSS}
     \item
     \textbf{Technologies}: {.NET Core, .NET Framework, Angular, Docker, Kubernetes, Rancher, GitLab CI/CD, GitHub Actions, DevExpress, Selenium, Playwright, Umbraco CMS, ELK Stack (Elasticsearch, Logstash, Kibana), Stripe API, OpenAI API, Firebase (Auth, Firestore), Azure, AWS, Google Cloud}
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
